### 2014-12-01 writing/F'14 paper/sick.tex
SICK commentary update.

Despite the small amount of high quality training data available, it is possible to train our model to perform competitively on textual entailment. Our performance did not reach the state of the art (84.6\%), but exceeded the median submission to the competition (77.06\%) in a field including many models which used sophisticated hand-engineered features specific to the specific version of the entailment task at hand.

>>>>

Despite the small amount of high quality training data available and the lack of resources for learning lexical relationships (especially exclusion, as in \ii{cat}--\ii{dog}), it is possible to train our model to perform competitively on textual entailment. Our performance did not reach the state of the art (84.6\%), but exceeded the median submission to the competition (77.06\%) in a field including many models which used sophisticated hand-engineered features specific to the specific version of the entailment task at hand.
